Using traffic analysis to identify The Second Generation Onion Router

### 2011-06-26 thesis/results.tex
Unique name for stats table
Fixes from IEEE conference paper

\begin{table}[H]
  \begin{tabular}{lrrrrrr}
    \toprule
    Phase & Minimum & 1st Quartile & Median & Mean & 3rd Quartile & Max \\
    \midrule
    1 & 66 & 66 & 699 & 860.4 & 1514 & 1514\\
    2 & 66 & 66 & 652 & 760.3 & 1514 & 1514\\
    3 & 66 & 66 & 652 & 733.7 & 1514 & 1514\\
    \bottomrule
  \end{tabular}
  \caption{Summary of packet sizes}
  \label{table:packet_size_summary}
\end{table}

@@

\section{Conclusion}

Using Tor as a communications proxy incurs some overhead, sufficient enough
that when using a Tor proxy in controlled conditions, its traffic can be
distinguished from regularly encrypted traffic. This overhead may be sufficient
enough that Tor nodes in a real world network can be identified by using
readily available eavesdropping techniques.

However, this experiment was based on a small set of simulated data, with which
it would be impossible to cover all possible real world conditions. The
variability and noise present in the real Tor network may make this
classification technique impossible.

@@

>>>>

\begin{table}[H]
  \begin{tabular}{lrrrrrr}
    \toprule
    Phase & Minimum & 1st Quartile & Median & Mean & 3rd Quartile & Max \\
    \midrule
    1 & 66 & 66 & 699 & 860.4 & 1514 & 1514\\
    2 & 66 & 66 & 652 & 760.3 & 1514 & 1514\\
    3 & 66 & 66 & 652 & 733.7 & 1514 & 1514\\
    \bottomrule
  \end{tabular}
  \caption{Summary of packet sizes}
  \label{table:packet_size_statistics}
\end{table}

@@

\section{Conclusion and Future Research}

This research demonstrates that Tor does have characteristics that make it
distinguishable from regular encrypted traffic. The encryption used by Tor does
not appear to blur the size of communication cells sufficiently to prevent
automated identification of Tor traffic, even with only a few observed packets.
While the scope of this research is limited, it suggests that it may be
possible to build simple software to automatically identify Tor users and block
them from the network.

@@

Training a classifier against real world traffic will account for the different
and varied nature of packet switching hardware, with different maximum
transmission units, performance capabilities and geographic location.

The heuristic based classifier used in this paper used a single attribute: the
size of individual packets in a stream, to classify with great accuracy. But
other attributes may be considered, the most typical of these being inter
packet arrival time - though this is likely to be more affected by natural
variability.

The encrypted traffic generated in the first phase of the experiment, only
covered a single application and version. It may be possible that other
applications use the same protocol with encryption and have characteristics
similar to that produced by Tor. This would lead to any proposed classifier
generating false positives. Further research should also consider the nature
and characteristics of a wider set of encrypted communications.

### 2011-06-26 thesis/thesis.tex
Fixes from IEEE conference paper

While Tor has been the subject of much academic literature, the primary
objective of researchers has historically been the attempt to reveal participant
identities \parencite[3]{Murdoch:2005p325}.  Many attack techniques proposed
have been somewhat academic in nature and not necessarily feasible in practice
\parencite{Raccoon:2008fk}. Sometimes they require compromise of large parts of
the Tor network, supplying hostile data to Tor users or complicated knowledge of
usage patterns and an excess of patience. The technique demonstrated in this
thesis is a low cost technique, which does not require very sophisticated
equipment and can be completed by a passive observer.

>>>>

While Tor has been the subject of much academic literature
\parencite{Hopper:2007p347,Murdoch:2007p320,Herrmann:2009p1189}, the primary
objective of researchers has historically been the attempt to reveal
participant identities \parencite[3]{Murdoch:2005p325}.  Many attack techniques
proposed have been somewhat academic in nature and not necessarily feasible in
practice \parencite{Raccoon:2008fk}. In certain circumstances they require
compromise of large parts of the Tor network, supplying hostile data to Tor
users or complicated knowledge of usage patterns and an excess of patience. The
technique demonstrated in this paper is a low cost technique, which does not
require sophisticated equipment and can be completed by a passive observer.
